Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2023-05-31 docs/manuscript/saved_text.tex

>>>>

% Some saved language about survey biases from limitations (from Peter)
Without this knowledge and data, we have no way of knowing if an adjustment to our sample is likely to increase or decrease bias in our results.

Being unable to meaningfully differentiate subgroups for either stratification or post-stratification, we adopted a simple random sampling scheme and provide our data to facilitate transparency and reanalysis of our sample.
Considering these challenges, our results could be viewed as an exploratory analysis that identifies researcher characteristics that might differentiate subgroups with similar understandings of reproducibility, which could be used to stratify or post-stratify future reproducibility related research in geography.
Nonetheless, because we were unable to assess the representativeness of our sample our results may be subject to at least three forms of bias.

\textit{Exclusion Bias:} One limitation of our approach is that geographic researchers publish in a range of journals that are not necessarily indexed as geography by the Web of Science. 
Geographic researchers that have only published outside these indexed journals would not be captured in our sampling frame creating non-coverage errors in our sample. 
However, we believe the number of individuals falling into this category will be small as most active geographic researchers are likely to publish at least one study in one of the X geography journals used in our sampling frame over a 5-year period.

\textit{Self-selection Bias}. A related concern is that it may be the case that geographic researchers more familiar with reproducible research practices, or those working in subfields more involved with the current reproduciblity debate (e.g., quantitative, computational research) were more likely to respond to our survey. 
Conversely, it may also be the case that researchers working in subfields traditionally associated with critiques of a positivist scientific approach (e.g., qualitative, human geography) were less likely to participate in our survey. 
We attempted to partially quantify this issue by examining the characteristics of the 40 researchers who started our survey but did not complete enough of the survey to be included in the final analysis.
Taking into account 29 researchers who reported their subfield but did not complete the full survey, completion rates for all subfields were between 84 and 87 percent, except slightly higher rates for methods / GIScience (96.8\%).
Considering 31 researchers who reported their method but did not complete the full survey, completion rates were 84.2 percent for mixed methods, 87.0 percent for qualitative methods, and 91.1 percent for quantitative methods. 
These values suggest that self-selection was not a significant issue.
This analysis of course does not measure researchers who elected to never start the survey.

While we cannot definitively eliminate the possibility of self-selection bias from our survey, we believe its presence may be a limited concern because it is likely to only amplify some of our key findings. 
Namely, that reproducible research practices have yet to be widely adopted in the field and that relatively few geographers are attempting and sharing independent reproduction studies.
Nonetheless, we believe concerns about self-selection should motivate a closer examination of reproducibility within the subfields and approaches for which we obtained the smallest samples --- qualitative, human geography, and nature society.

\textit{Questionnare Bias:} Another potential limitation of our research is that we based our survey instrument on a review of prior reproducibility surveys and our identification of practices and barriers discussed in the reproducibility literature. 
To the extent that this literature over represents perspectives from selected disciplines, experimental research designs, and computationally-intensive research approaches our survey may reflect this bias. 
If this were the case, our survey may not gather data on practices and barriers important to the reproducibility of types of geographic research not like the work conducted in those disciplines that are well represented in the existing literature. 
To address this concern, we incorporated into our survey instrument questions informed by a parallel review of the reproducibility literature available within geography and a review of critiques of positivist science made by social scientists and human geographers.
We also provided the option for an open ended text response to questions about reproducible research practices, researcher familiarity with those practices, and barriers to reproducibility in an attempt to identify factor and issues we did not anticipate during instrument construction.
